Analyzing the impact of social attributes on the success of commit integration

### 2017-02-17 Paper/MSRChallenge2017.tex
added the results

\begin{table*}[ht]
\centering
\begin{tabular}{l||r|r||r|r}
  & \multicolumn{2}{|c||}{Original number of instances}  & \multicolumn{2}{|c}{Downsampled} \\
\hline
  & Technical & Technical and Social & Technical & Technical and Social \\
\hline
\textbf{Correctly Classified Instances}&  77.01\% & 81.10\%  & 64.10\% & 76.09\%\\

@@

>>>>

\subsection{Success Classification}
\begin{table*}[ht]
\centering
\begin{tabular}{l||r|r||r|r}
  & \multicolumn{2}{|c||}{Original number of instances}  & \multicolumn{2}{|c}{Downsampled} \\
\hline
  & Technical & Technical and Social & Technical & Technical and Social \\
\hline
\textbf{Correctly Classified Instances}&  77.01\% & 81.10\%  & 64.10\% & 76.09\%\\

@@

Table~\ref{resultsTable} shows the results of running the data sets through the
default Weka J48 decision tree algorithm. 
In the original data set, 74.43\% of the builds were successful, the rest were not
successful.  This means that a classifier which guesses successful every time
would produce a classification rate of 74.43\%. The decision tree built from
only the technical indicators has a correct classification rate of 77.01\%, so
the technical attributes only increased the prediction accuracy by about 3\%.
Adding the social data increased the classifier's accuracy from 77.01\% to
81.10\%, about a 4\% increase.

On the downsampled data, the decision tree created from the technical attributes
had a classification accuracy of 64.10\%, when predicting a successful build in
all instances would produce 50.00\% accuracy.  After including the social data
in the data set, the classifier correctly predicted 76.09\% of the data set,
about a 12\% improvement from only the technical data.

The same

\subsection{Build success by core team member}

For the build success investigation, we classified the build success rate for
core team members and non-core team members.  We found that core team members
triggered of 89.39\% of the builds in the data set and 75.58\% of those builds
passed.  Non-core team members triggered 10.61\% of the builds in the data set
and 64.70\% of the builds passed.
